Artificial Intelligence Course Report

### 2018-01-14 paper/Zhenghui/paper.tex
minor

\subsection{Deep Neural Network}
Deep learning \cite{Deeplearning} has been shown as a successful machine learning method for a variety of tasks. In our work, we use a deep neural network with fully-connected multilayer structure both on PCA-processed data and on raw data with \textbf{greedy layer-wise pre training}. Besides, we add L2 regularization in each fully-connected layer to avoid overfitting and control the model complexity.
\subsubsection{network structure} Since the features do not have any locality or direct relationship, we don¡¯t use convolutions.\\

\begin{itemize}
	\item \textbf{NN on PCA-processed data}\\
	In this model, firstly we use PCA-processed data (500-dimension) as our network input. Then we add hidden layer1(256-dimension), hidden layer2(512-dimension), hidden layer3(256-dimension), finally a output layer.  The structure is shown as Figure~\ref{nn_1} network \romannumeral1. 
	For weight initialization, we initialize each neurons weight vector as a random vector sampled from a multi-dimensional gaussian. For bias initialization, we set the bias vectors all to $0$. We initialize our weight with the consideration that the size of our network is limited and it can be trained easily according to the network \romannumeral2.

@@

\subsubsection{Regularization}
We use L2 regularization in each fullt-connected layer.It can be implemented by penalizing the squared magnitude of all parameters directly in the objective. For every weight $w$ in the network, we add the term $1/2¦Ëw$ to the objective, where ¦Ë is the regularization strength. This can help control the capacity of neural networks to prevent overfitting.

>>>>

\subsection{Deep Neural Network}
For a variety of tasks, deep learning \cite{Deeplearning} has been shown as a successful approach. We use a deep neural network (NN) with multiple fully-connected layer structure in our work. The NN is trained on Both PCA-processed data and raw data with \textbf{greedy layer-wise pre training}. Moreover, an L2 regularization is employed in each fully-connected layer to avoid overfitting and control the model complexity.
\subsubsection{network structure} Since the features do not have any locality or direct relationship, we don't use convolutions.\\

\begin{itemize}
	\item \textbf{NN on PCA-processed data}\\
	In this model, first, we use PCA-processed data (500-dimension) as the input. Then we add hidden layer1 (256-dimension), hidden layer2 (512-dimension), hidden layer3 (256-dimension), finally a output layer. The structure is shown in Figure~\ref{nn_1} network \romannumeral1.

	For weight initialization, we initialize each neurons weight vector as a random vector sampled from a multi-dimensional gaussian. For bias initialization, we set all the bias vectors to $0$. We initialize our weight with the consideration that the size of our network is limited and it can be trained easily according to the network \romannumeral2.

@@

\subsubsection{Regularization}
We use L2 regularization in each fullt-connected layer.It can be implemented by penalizing the squared magnitude of all parameters directly in the objective. For every weight $w$ in the network, we add the term $1/2\lambda w^2$ to the objective, where $\lambda$ is the regularization strength. This can help control the capacity of neural networks to prevent overfitting.
